\chapter[Milestones]{Research Plan}

\label{Chap:Milestones}

\section{Milestones}
To track the development of the project, a set of milestones have been established with consideration of assessable dates. 
Table \ref{tab:milestones} below outlines the milestones for the work and what is required for each phase.
Emboldened text indicates an assessable milestone.


\begin{center}
    \small
    \begin{longtable}{p{0.25\linewidth}p{0.5\linewidth}p{0.15\linewidth}}
        \caption{Milestones} \\
        \label{tab:milestones} \\
        \toprule
        Milestone & Description & Date \\
        \midrule
        \endfirsthead
        
        \caption{Milestones (continued)} \\
        \toprule
        Milestone & Description & Date \\
        \midrule
        \endhead
        
        \bottomrule
        \multicolumn{3}{r}{\textit{Continued on next page}} \\
        \endfoot
        
        \bottomrule
        \endlastfoot
        
        \textbf{Project Proposal}	& Complete the project proposal and literature review.                                              & 23/4 \\
        Configure hardware			& Implement NEORV32 processor on FPGA, connect to external components through wishbone interface.   & 23/4 \\
        \textbf{Seminar}            & Present the current project status.                                                               & 23/4 \\
        Image detection algorithm   & Select and implement image detection algorithm in hardware.                                       & 23/4 \\
        VGA driver                  & Develop driver and interface to display processed image on VGA monitor.                           & 23/4 \\
        Benchmark                   & Benchmark system performance against related works.                                               & 23/4 \\
        \textbf{Demo}               & Demonstrate the complete project.                                                                 & 23/4 \\
        \textbf{Thesis}             & Document and write project results.                                                               & 23/4 \\
    \end{longtable}
\end{center}


\nopagebreak


\section{Risk Assessment}
This project is conducted in the low-risk laboratory covered by general OHS laboratory rules.